### 2018-11-12 papers/journal/problem.tex
removed some spaces
Updated introduction section: Biological part is still in early writing stage. Incomplete update

\subsection{SMT}

\paragraph{Search problem}
Based upon earlier discussion, we need to answer the following search
question among VTSs.
For a given $k$, size $\nu$, and molecule number $\mu$,
we are searching for well-structured, stable, and well-fused VTS
$G = (\nodes,\mols,\edges,\nlabel,\pairs,\edgef,\nodef)$ such that
$|\nodes| = \nu$, $|\mols| = \mu$, and
$G$ is not $k$-connected.

\subsection{BMC}
The notion of stability and connectivity varies slightly for BMC encoding.

%
We call $G$ {\em stable} if for each $(n,M',n') \in \edges$ and $m \in M'$,
there exists a $m$-path in G with $n_1 = n'$ and $n_\ell = n$.
%

%
We call $G$ {\em connected} if for each $n,n' \in \nodes$,
$n'$ there is a path from $n$ to $n'$ in G.
%
We call $G$ $k$-connected if for each $\edges' \subseteq \edges$ and $|\edges'| < k$,
VTS $(\nodes,\mols,\edges-E',\nlabel,\pairs,\edgef,\nodef)$ is connected.
%

@@

For the experimentation, we will restrict ourselves to the cycles of length one. 
%
This restriction puts an upper limit of N on the length of each searched path. 
%
Creating a formula to search a path of length N for each molecule m on every edge E will be extremely large and harder for the solvers to handle.  
%
Even if there exist shorter paths we have to create the formula of maximum size N. 
% 
To resolve the these problems we will use a technique called bounded model checking, where the depth of the path can be specified and consequently increased or decreased.  
%
This specified depth is called unwinding in the technical terms.
%and can be specified for each path separately.

\paragraph{Search problem}
Based upon earlier discussion, we need to answer the following search
question among VTSs.
For a given $k$, size $\nu$, molecule number $\mu$, and unwinding depth w,
we are searching for well-structured, stable, and well-fused VTS
$G = (\nodes,\mols,\edges,\nlabel,\pairs,\edgef,\nodef)$ such that
$|\nodes| = \nu$, $|\mols| = \mu$, and $G$ is not $k$-connected with w length of unwinding.

>>>>

\subsection{SMT}
\paragraph{Search problem}
Based upon earlier discussion, we need to answer the following search
question among VTSs.
For a given $k$, size $\nu$, and molecule number $\mu$,
we are searching for well-structured, stable, and well-fused VTS
$G = (\nodes,\mols,\edges,\nlabel,\pairs,\edgef,\nodef)$ such that
$|\nodes| = \nu$, $|\mols| = \mu$, and
$G$ is not $k$-connected.

\subsection{BMC}
%The notion of stability and connectivity varies slightly for BMC encoding. 
In this subsection, we will present the concept of stability and connectivity for BMC encoding.

%
We call a graph $G$ {\em stable} if for each $(n,M',n') \in \edges$ and $m \in M'$,
there exists a $m$-path in G with $n_1 = n'$ and $n_\ell = n$.
%

%
We call a graph $G$ {\em connected} if for each $n,n' \in \nodes$,
$n'$ there is a path from $n$ to $n'$ in G.
%
We call a graph $G$ $k$-connected if for each $\edges' \subseteq \edges$ and $|\edges'| < k$,
VTS $(\nodes,\mols,\edges-E',\nlabel,\pairs,\edgef,\nodef)$ is connected.
%

@@

For the experimentation, we will restrict ourselves to the elementary cycles (cycles of length one). 
%
This restriction puts an upper limit of N-1 on the length of each searched path. 
%
Creating a formula to search a path of length N-1 for each molecule m on every edge E will be extremely large and harder for the solvers to handle.  
%
Even if there exist shorter paths we have to create the formula of maximum size N-1. 
% 
To resolve these problems we will use a technique called bounded model checking, where the depth of the path can be specified and consequently increased or decreased.  
%
This specified depth is called unwinding in the technical terms.
%and can be specified for each path separately.

\paragraph{Search problem}
Based upon earlier discussion, we need to answer the following search
question among VTSs.
For a given $k$, size $\nu$, molecule number $\mu$, and unwinding depth w,
we are searching for well-structured, stable, and well-fused VTS
$G = (\nodes,\mols,\edges,\nlabel,\pairs,\edgef,\nodef)$ such that
$|\nodes| = \nu$, $|\mols| = \mu$, and $G$ is not $k$-connected with w depth of unwinding.
